Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-06-04 article.tex
Improve abstract

\begin{abstract}
Understanding how the brain works is a key to understand and to treat
brain pathologies and disorders such as Parkinson's disease, epilepsy.
Retrieving the connectomes, neurons connectivity map, will shed new lights on
the anatomical and functional connectivity of the brain.
The connectomics challenge

@@

\begin{keywords}
List of keywords
\end{keywords}

>>>>

\begin{abstract}
Understanding how the brain works is a key to understand and to treat
brain pathologies and disorders such as Parkinson's disease, epilepsy.
Retrieving the connectomes, neurons connectivity map, will shed new lights on
the anatomical and functional connectivity of the brain.
In the context of the Connectomics challenge, we propose a pre-processing and a simple approach in order to achieve a high performance inference of the connectivity network.
We put in perspective our method by comparing with other inference method such as GTE [], another method proposed to infer a neural network from calcium fluorescent imaging, and Genie3 [], a tree-based approach very competitive in several gene inference challenge (i.e. DREAM4 and DREAM5).\\

% Discussion on the metrics?

@@

\begin{keywords}
Network inference - Precision matrix - GENIE3
\end{keywords}
